\Large Plotting the Single-Electron Solution to Schr\"{o}dinger's Equation with OpenCL

### 2010-05-06 paper/paper.tex
More in the future work section

The generating differential equations for these polynomials are as follows:

@@

where $\tilde{F}$ is Gauss' hypergeometric function, which we don't care about since we're simply allowing Mathematica to evaluate it and using the comparatively simple symbolic results in our table.

@@

Each benchmark point is the minimum of five trials.

@@

There are quite a few things which have come up while developing this project that would be interesting to implement if we were to continue work on the codebase.

@@

Section \ref{cameraTransformation} covered the ideal solution to the problem of comprehending the shape of the orbital from our 2D representation --- however, if that solution proved to be too challenging, one could instead generate an animation of slices through the cloud, each slice being similar to figure \ref{fig:slice}

@@

@@

>>>>

The generating equations for these polynomials are as follows:

@@

where $\tilde{F}$ is Gauss' hypergeometric function, which we don't need to bother ourselves with since we're simply allowing Mathematica to evaluate it and using the comparatively simple symbolic results in our table.

@@

Three computers have spent countless hours performing calculations to bring you the following results, as each benchmark point is the minimum of five individual trials.

@@

There are quite a few things which have come up while developing this project that would be interesting to implement if we were to continue work on the codebase. We will discuss a few of these below:

@@

Section \ref{cameraTransformation} covered the ideal solution to the problem of comprehending the shape of the orbital from our 2D representation --- however, if that solution proved to be too challenging, one could instead generate an animation of slices through the cloud, each slice being similar to figure \ref{fig:slice}. This would provide another form of interesting visualization of the resulting data.

@@

A third way to make the visualization more appealing (or even more informative) would be to provide some manner of colorization. One potential algorithm would be to colorize each sample based on its depth in $z$; the resulting image would then have more depth information, which might increase the ease with which it is interpreted. A variety of other coloring functions are possible, but none were pursued during this project, for time's sake.

@@

Equations \ref{laguerre} and \ref{legendre} provide a generalized way to construct Laguerre and Legendre polynomials, respectively. However, our implementation does not make use of these functions, instead using a table of simplified solutions, generated with Mathematica, which is limited in scope.

The length of the table determines the range of $n, l, m$ values which can be passed into our program, and is the only restriction on generality within our implementation. If one were to construct these functions on the fly from their generating equations, the algorithm would be completely generalized in terms of $n, l, m$, and would be significantly more useful from an exploratory standpoint.

However, as discussed in section \ref{laguerreLegendre}, this would require (at least) the implementation of a symbolic differential equation solver in OpenCL, which could potentially be a very time-consuming task (it could also increase the number of GPU stream processors per kernel required, significantly decreasing the speedup gained).

Alternatively, one could write a translation program to automatically generate the table from Mathematica, removing the slow, error-prone human translation step, and very quickly expand the size of the table to something more useful.
